Bayesian Neural Networks

### 2024-04-18 Paper/paper.tex
Updated report

\section{Introduction}

@@

We used the following hyperparamaters for training:
\begin{figure}[H]
	\begin{center}
	\begin{tabular}{|c||p{3cm}|p{3cm}|} % Adjust p{width} as needed
	\hline
	\textbf{Hyperparameter} & \textbf{CNN} & \textbf{BCNN} \\ [0.5ex] 
	\hline\hline
	Epochs & 100 & 100\\
	\hline
	Learning Rate & 0.001  & 0.003  \\
	\hline
	Regularization Rate& 0.001 & 0.001 \\
	\hline
	Optimizer & Adamw  & Adamw  \\
	\hline
\end{tabular}
\end{center}
\end{figure}

In addition to the hyperparamaters above, the two models have the same number of layers and levels. We did not adjust the priors, as those were set by the BCNN layer code from \cite{shridhar2018uncertainty}.

@@

Additionally, neither model converged with the train and validation accuracy, this is an indication that we might need to increase the regularization rate. Another thing to note from figure \ref{fig:train-v-val} is that the BCNN took longer to divirge from the train accuracy.

\begin{figure}[H]
	\centering
	\begin{subfigure}{\textwidth}
		\centering
		\includegraphics[width=.9\linewidth]{../Images/CNN_confusion_matrix}
		\caption{CNN}
	\end{subfigure} \\% //  
	\begin{subfigure}{\textwidth}
		\centering
		\includegraphics[width=.9\linewidth]{../Images/BNN_confusion_matrix}
		\caption{BCNN}
	\end{subfigure}
	\caption{Confusion matrices}
\end{figure}

The two models have the same set of confusions

\section{Closing}

>>>>

@@

We choose to keep the number of layers and levels in the model the same to keep the models roughly equal, but tuned the hyperparamaters seperately. We did not adjust the priors on the BCNN, as those were set by the BCNN layer code from \cite{shridhar2018uncertainty}. We found the following hyperparemeters to created the best model:

\begin{figure}[H]
	\begin{center}
	\begin{tabular}{|c||p{3cm}|p{3cm}|} % Adjust p{width} as needed
	\hline
	\textbf{Hyperparameter} & \textbf{CNN} & \textbf{BCNN} \\ [0.5ex] 
	\hline\hline
	Epochs & 100 & 100\\
	\hline
	Learning Rate & 0.001  & 0.003  \\
	\hline
	Regularization Rate& 0.001 & 0.001 \\
	\hline
	Optimizer & Adamw  & Adamw  \\
	\hline
\end{tabular}
\end{center}
\end{figure}

@@

Based on the divergent lines in figure \ref{fig:train-v-val}, the model needs tuning. Specifically, the regularization rate needs to be raised. One interesting thing that appears in the figures, is that the BCNN took longer to diverge from the train accuracy compared to CNN.

\begin{figure}[H]
	\centering
	\begin{subfigure}{\textwidth}
		\centering
		\includegraphics[width=.9\linewidth]{../Images/CNN_confusion_matrix}
		\caption{CNN}
	\end{subfigure} \\% //  
	\begin{subfigure}{\textwidth}
		\centering
		\includegraphics[width=.9\linewidth]{../Images/BNN_confusion_matrix}
		\caption{BCNN}
	\end{subfigure}
	\caption{Confusion matrices}
	\label{fig:confusion}
\end{figure}

Based on the confusion matrix from two models in \ref{fig:confusion}, the two models confuse similar sets of classes. Both models struggle to differentiate animals, but the BCNN has poorer accuracy on the classes that are easily confused.
